SunPy - Python for Solar Physics

### 2014-01-24 3-1-VSO.tex

\begin{listing}[h]
\begin{minted}{pycon}
>>> from sunpy.net import vso
>>> client=vso.VSOClient()
>>> tstart, tend = '2011/6/7 05:30', '2011/6/7 10:30'

@@

\begin{listing}[h]
\begin{minted}{pycon}
>>> pathformat = '/data/{instrument}/{detector}/{file}.fits'
>>> results = client.get(coronographs, 
...                      path = pathformat)

>>>>

\begin{listing}[h]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net import vso
>>> client=vso.VSOClient()
>>> tstart, tend = '2011/6/7 05:30', '2011/6/7 10:30'

@@

\begin{listing}[h]
\begin{minted}[bgcolor=bg]{pycon}
>>> pathformat = '/data/{instrument}/{detector}/{file}.fits'
>>> results = client.get(coronographs, 
...                      path = pathformat)
